Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-30 volunteer-clouds-ieee-ci-si.tex
some comments

There is, then, space for systems that do not have any of those
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. NodIO is first an application that
runs in two tiers, a server and a client that can be possibly run on a
browser. As such, it can be run in any computer that loads the web
page where the client is embedded, including possibly many over which
the scientist has no control.

When faced with the problem of diminishing funds for buying new
hardware and continuous hardware failures of existing clusters and
taking into account our experience of working with web applications,
including JavaScript, from the beginning and other volunteer and
unconventional distributed evolutionary computing systems, our group
decided to create a new free framework that would allow anyone to
create a volunteer distributed EC experiment using cloud resources as
servers and browsers as clients.

>>>>

There is, then, space for systems that do not have any of those
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. NodIO is first an application that
runs in two tiers, a server and a client that can be possibly run on a  % [Pedro] Both the server and the client in browsers? different browsers as I understand?
browser. As such, it can be run in any computer that loads the web
page where the client is embedded, including possibly many over which
the scientist has no control.

When faced with the problem of diminishing funds for buying new     % [Pedro] This sentence is so so long. I would split it in two sentences.
hardware and continuous hardware failures of existing clusters and
taking into account our experience of working with web applications,
including JavaScript, from the beginning and other volunteer and
unconventional distributed evolutionary computing systems, our group
decided to create a new free framework that would allow anyone to
create a volunteer distributed EC experiment using cloud resources as
servers and browsers as clients.
